\begin{thebibliography}{99.}

\bibitem{01} Arjen K. Lenstra, James P. Hughes, Maxime Augier, Joppe W. Bos, Thorsten Kleinjung, Christophe Wachter: Ron was wrong, Whit is right, https://eprint.iacr.org/2012/064.pdf (2012)

\bibitem{02} Kerry Scharfglass, Darrin Weng, Joseph White, Christopher Lupo, Breaking weak 1024-bit RSA keys with CUDA, https://digitalcommons.calpoly.edu/cgi/viewcontent.cgi? referer=https://scholar.google.com/\&httpsredir=1\&article=1241\&context=csse\_fac

\bibitem{03} Cloostermans B., Quasi-linear GCD computation and factoring RSA moduli, Eindhoven University of Technology, Department of Mathematics and Computer Science, Bachelor Mathematics (2012)

\bibitem{04} Heninger N., Durumeric Z., Wustrow E., Halderman J. A., Mining Your Ps and Qs: Detection of Widespread Weak Keys in Network Devices, 21 st Security Symposium Security’12, ISBN 978-931971-95-9, Bellevue, WA, pp. 205—220 (2012)

\bibitem{18} Arjen K. Lenstra, James P. Hughes, Maxime Augier, Joppe W. Bos, Thorsten Kleinjung, and Christophe Wachter, “Ron was wrong, Whit is right”, I\&C - School of Computer and Communication Sciences - LACAL - Laboratory for cryptologic algorithms, https://eprint.iacr.org/2012/064.pdf, (2012).

\bibitem{19} Kerry Scharfglass, Darrin Weng, Joseph White, Christopher Lupo, "Breaking weak 1024-bit RSA keys with CUDA", California Polytechnic State University, Dec 2012, Publisher: IEEE, DOI: 10.1109/PDCAT.2012.58ISBN: 978-0-7695-4879-1

\bibitem{05} Li C., Zhang J., Sang L., Gong L., Wang L., Wang A., Wang Y., Deep Learning- Based Security Verification for a Random Number Generator Using White Chaos, Entropy, 22, 1134; doi:10.3390/e22101134 (2020)

\bibitem{06} Singh S., Maakar S. K. and Kumar S., A Performance Analysis of DES and RSA Cryptography, International Journal of Emerging Trends \& Technology in Computer Science (IJETTCS), Volume 2, Issue 3, ISSN 2278-6856 (2013)

\bibitem{07} Velizar Shalamanov, Vladimir Monov, Ivaylo Blagoev, Silvia Matern, Gergana Vassileva, Ivan Blagoev, A Model of ICT Competence Development for Digital Transformation. ISSN 0861-5160 (print), ISSN 1314-2119 (online) (2020)

\bibitem{20} Julian Jang-Jaccard and SuryaNepal, “A survey of emerging threats in cybersecurity,” Journal of Computer and System Sciences 80, no. 5 (2014): 973-993. 

\bibitem{08} Jang-Jaccard J., Nepal S., A survey of emerging threats in cybersecurity. Journal of Computer and System Sciences, 80(5), 973-993 (2014)

\bibitem{09} Kostadinov G., Atanasova T., Security Policies for Wireless and Network Infrastructure. Problems of Engineering Cybernetics and Robotics, vol. 71, 14-19, Bulgarian Academy of Sciences (2019)

\bibitem{10} Dineva, K., Atanasova, T.: Regression Analysis on Data Received from Modular IoT System. ESM’2019, EUROSIS-ETI, ISBN: 978-9492859-09-9, EAN: 9789492859099, pp.114-118, 2019

\bibitem{11} DiCarlo D., Random Number Generation: Types and Techniques, Liberty University, (2012)

\bibitem{12} Jin, A., Ling, D., Goh A., Biohashing: Two factor authentication featuring fingerprint data and tokenised random number. Pattern Recognition, 37, 2245- 2255. (2004)

\bibitem{13} Ergün S., Security analysis of a chaos-based random number generator for applications in cryptography, 15th International Symposium on Communications and Information Technologies (ISCIT), pp. 319-322, doi: 10.1109/ISCIT.2015.7458371 (2015)

\bibitem{14} Ryabko B., Astola J., Malyutov M., Compression-Based Methods of Statistical Analysis and Prediction of Time Series, Springer International Publishing Switzerland, eBook ISBN 978-3-319-32253-7 (2016)

\bibitem{15} Trappe, L., Washington, L. Introduction to cryptography with coding theory (2nd ed). Upper Saddle River, NJ: Pearson (2006)

\bibitem{16} Hart J. D., Roy R. and Murphy T. E., Optical random number generation - harvesting entropy from noise and chaos, 51st Annual Conference on Information Sciences and Systems (CISS), doi: 10.1109/CISS.2017.7926165 (2017)

\bibitem{17} Lavasani, A., Eghlidos, T. Practical next bit test for evaluating pseudorandom sequences. Scientia Iranica, 16(1), 19-33 (2009)

\bibitem{21} Dichtl, M. How to predict the output of a hardware random number generator. CHES 2003, 2779, 181-188. (2003) Dichtl, M. How to predict the output of a hardware random number generator. CHES 2003, 2779, 181-188. (2003).

\bibitem{22} Carr J., Simple random number generation, Computers \& Geosciences, 29(10):1269-1275 (2003).

\bibitem{23} L’Ecuyer P., Random Number Generation, In book: Handbook of Simulation: Principles, Methodology, Advances, Applications, and Practice (2007)

\bibitem{24} Camara C., Martín H., Peris-Lopez P., Aldalaien M., Design and Analysis of a True Random Number Generator Based on GSR Signals for Body Sensor Networks, Sensors 19, 2033; doi:10.3390/s19092033 (2019)

\end{thebibliography}
